Efficient Feasibility Checking Algorithm of Photovoltaic Array Reconfiguration

### 2019-12-19 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-19 17-01-01

\subsection{Outline of the algorithm}\label{sec:outline-algorithm}
\subsection{Algorithm}\label{sec:algorithm}
\section{Experiment Results}\label{sec:experiment-results}
\section{Conclusion}\label{sec:conclusion}
The conclusion goes here.

>>>>

\subsection{Outline of the algorithm}\label{sec:outline-algorithm}
In a PV array with $s$ PV strings.
For a given current sequence $Q = (Q_{1},Q_{2},\ldots ,Q_{s})$ $(Q_{i} \geq Q_{j} \mbox{\ if\ } i \leq j)$, we will assign PV panels to strings in the order of $Q_{1},Q_{2},\ldots ,Q_{s}$.
In this step, we will consider how much we lose an opportunity that the panel is more effectively used for the next current level.
For example, as the PV panel shown in Table~\ref{tab:NumofModules} which contain three PV modules.
2 of 3 modules are able to working at current level of $Q_{1}$ and $Q_{2}$.
All 3 modules are able to activate at current level $Q_{3}$.
Thus, if this panel been selected working for a PV string at current level $Q_{1 or 2}$ , two-third of modules are able to deliver energy while the remaining one module been bypassed.
We consider the ``$loss$'' that how many PV modules we fail to use in other current level and the ``$gain$'' that how many PV modules we can activate in the target current level together.
Since two parameter are considered in the selection process, they can minimize ``$loss$'' while minimizing the number of selected PV panels.
% In this algorithm, we select PV panels as so to minimize the $loss$ and maximize the $gain$.
\begin{table}[tbp]
  \caption[]{}
  \label{tab:NumofModules} 
  \centerline{Maximum number of activate PV modules}
  \vskip5pt
  \begin{center}
  \begin{tabular}{c|c|c|c}
    \hline
    Current level                 & $Q_{1}$ & $Q_{2}$ & $Q_{3}$  \\ \hline
    Number of activate PV modules & 2  & 2    & 3        \\ \hline
  \end{tabular}
  \end{center}
\end{table}
In this algorithm, we choose $Loss-rate$ to give selection priority.
The $Loss$-$rate$ is the difference of active modules in panel $p$ for the target current level $Q_n$  in current sequence $Q$ with other current levels per module.
Let $M_{p}(I)$ denote the number of PV modules that can be active at current level $I$ in panel $p$.
In a $s$ strings PV array, $Loss-rate$ for panel $p$ of target current level $n$ on $k$-th current level $Q_{k}$ ($2 \leq k \leq s$) is shown as follow.
\begin{equation}\label{eq:4}
    Loss\mbox{-}rate(p,n,k) =
    \begin{cases}
    \frac{M_{p}(Q_{k})-M_{p}(Q_{n})}{M_{p}(Q_{n})} & \mbox{if } M_{p}(Q_{n}) \neq 0 \\
    \infty & \mbox{if } M_{p}(Q_{n}) = 0
  \end{cases}
\end{equation}

For example, as the panel $p$ in Table~\ref{tab:NumofModules} $Loss-rate(p,Q_{1},Q_{2})=0$, $Loss-rate(p,Q_{1},Q_{3})=0.5$, that is, for target current level $Q_{1}$ there is no ``$loss$'' for current level $Q_{2}$ and only loss ``0.5'' active module for current level $Q_{3}$.

To assign panels of target current level $n$ to $n$-th string, the following step are applied.
Let $m$ be the required number of active modules per-string.
\begin{enumerate}
\item\label{step:1} Sort un-selected panels in a lexicographically ascending order of $Loss$-$rate(p,n,n+1)$, $Loss$-$rate(p,n,n+2)$,$\dots,$ $Loss$-$rate(p,n,s)$ and  lexicographically descending order of $M_p(Q_n)$.
\item\label{step:2} Selects sorted panels one by one until reaching the required number of active modules $m$.
  In step 2, panel with no active modules is skipped.
\item\label{step:3} Optimize the number of active modules.
  In step 3, if the number of selected active modules exceeds the required number $m$, redundant panels will be removed if exist.
\end{enumerate}

\subsection{Algorithm}\label{sec:algorithm}
\section{Experiment Results}\label{sec:experiment-results}
\section{Conclusion}\label{sec:conclusion}
The conclusion goes here.
